---
title: "R Markdown Presentation & Plotly"
author: "Rudra Patel"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Objective

Create a web page presentation using R Markdown that features a plot created with Plotly. Host your webpage on either GitHub Pages, RPubs, or NeoCities. Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. We would love to see you show off your creativity! Review criteria

The rubric contains the following two questions:

1. Does the web page feature a date and is this date less than two months before the date that you’re grading this assignment?
2. Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?

##Web Page date and Time
```{r time}
Sys.time()
```
```{r date}
Sys.Date()
```
##Plots

```{r add package}
library(plotly)
```



```{r plot graph}
plot_ly(z=volcano, type="surface")
```


```{r}
library(plotly)

plot_ly(
  type = "choropleth",
  locationmode = "country names",
  locations = c("India", "United States", "Brazil"),
  z = c(120, 180, 80),
  colorscale = "Viridis"
)

```